%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Professional Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}


%---------------------------------------------------------
 \cventry
    {\ulhref{https://kwantis.com}{Kwantis}} % Organization
    {Software Engineer (ML)} % Job title
    {Milan, Italy} % Location
    {Fall 2021 - Summber 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Creating, deploying, and leading time-series ML projects on oil and gas real live data}
      \end{cvitems}
    }

%---------------------------------------------------------
 \cventry
    {\ulhref{https://cafebazaar.ir/app?l=en}{Cafe Bazaar} and \ulhref{http://balad.ir/}{Balad Maps} (both are managed by \ulhref{https://hezardastan.net/}{Hezardastan holding})} % Organization
    {Software Engineer and Data Scientist} % Job title
    {Tehran, Iran} % Location
    {Spring 2016 - Summer 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Was a Software Engineer at Cafe Bazaar, which is the most popular and successful Android application store in Iran.}
        \item {A member of the Inline Apps team and the App Discovery team (while handling more than 300000 requests per hour).}
        % \item {Interviewed many people to help Cafe Bazaar with the hiring process.}
        \item {Developed an admin panel for the executive team of Cafe Bazaar, using Python Django, HTML, CSS, and Javascript.}
        % \item {Designing UI/UX of some of inline apps platform components and implementing them using Android programming.}
        \item {Developed a platform for Android developers to create Android apps, which there is no installation needed for them.}
        \item {Was a Data Scientist at Balad, which is the most popular maps and navigation application in Iran.}
        \item {Wrote some ETLs and Improved the traffic prediction accuracy using time series forcasting models and PySpark (on big data servers).}
%        \item {Determined the possible locations of speed bumps and traffic lights of Tehran while storing users' GPS locations on big data servers.}
        \item {Used Variational Autoencoders in PyTorch, planar graphs, R-trees, etc., on real large (20+ GB) datasets.}
        \item {Interviewed many people and helped Balad set the hiring process (as a member of the hiring committee).}
      \end{cvitems}
    }


% %---------------------------------------------------------
%   \cventry
%     {Software Developer and UI/UX Designer} % Job title
%     {\ulhref{http://www.sabzbiomedicals.com/}{Sabz Biomedicals}} % Organization
%     {Tehran, Iran} % Location
%     {Summer 2015 - Summer 2016} % Date(s)
%     {
%       \begin{cvitems} % Description(s) of tasks/responsibilities
%         \item {Using Embarcadero RAD Studio Delphi IDE for developing softwares which are used in biological laboratories equipments and have touch screens.}
%         % \item {Used Canon cameras API for imaging of nucleic acid and protein.}
%         \item {Using Canon cameras API and processing images for the recognition of captured DNA bands.}
%       \end{cvitems}
%     }


%---------------------------------------------------------
\end{cventries}
