%-------------------------------------------------------------------------------
% SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Research Experience}


%-------------------------------------------------------------------------------
% CONTENT
%-------------------------------------------------------------------------------
\begin{cvprojects}

%---------------------------------------------------------
  \cvproject
    {Detecting Unnecessary Code, as a Research Intern at \ulhref{https://www.kth.se/en}{KTH Royal Institute of Technology}}
    {}
    {}
    {Summer 2020 (Stockholm, Sweden)}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {This research internship was done under supervision of \ulhref{https://scholar.google.com/citations?user=dJQf4SYAAAAJ&hl=en}{Prof. Monperrus} for using graphs and machine learning in program analysis.}
        \item {I analyzed static call graph to detect the part of code that can be used or not, but definitely is not required for the application.}
        \item {I designed a framework for Java programmers, which is available on \ulhref{https://github.com/erfaniaa/gardgir}{GitHub}.}
      \end{cvitems}
    }
%---------------------------------------------------------

%---------------------------------------------------------
  \cvproject
    {Thatcher Illusion and Its Effects on the Face Recognition Problem (Using VGGFace2)} % Job title
    {} % Organization
    {} % Location
    {2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {I am a member of Shahid Beheshti University Computer Vision Group.}
        \item {Awarded as the best bachelor's thesis project in the university.}
        \item {The paper is being prepared to be submitted on \ulhref{https://journals.sagepub.com/home/pec}{Perception Journal}, under supervision of \ulhref{https://scholar.google.com/citations?user=trWxrgcAAAAJ&hl=en}{Prof. Ebrahimi Moghadam}.}
        \item {A small part of its source code is available on \ulhref{https://github.com/erfaniaa/thatcher-effect-dataset-generator}{GitHub}.}
      \end{cvitems}
    }
%---------------------------------------------------------

%---------------------------------------------------------
  \cvproject
    {Supervised and Unsupervised Methods for Satellite Images Super Resolution} % Job title
    {} % Organization
    {} % Location
    {2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Was done for Balad Maps to create larger satellite images for Iran maps and to be used in production.}
        \item {I compared different methods on real large (300+ GB) datasets, based on PSNR metric.}
      \end{cvitems}
    }
%---------------------------------------------------------

%---------------------------------------------------------
  \cvproject
    {Using Planar and Bipartite Graphs for Map Merging} % Job title
    {} % Organization
    {} % Location
    {2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {This research was done under supervision of \ulhref{https://scholar.google.ca/citations?user=7Eng5oAAAAAJ&hl=en}{Prof. Amin Gheibi} as a computational geometric problem.}
        \item {Our purpose was to merge two maps of a city by modeling them to graphs and polygons (using NumPy, Matplotlib, and NetworkX).}
        \item {I presented this research as a \ulhref{https://bit.ly/35XELVq}{guest speaker at the 21th ACM-ICPC Asia Tehran Regional Contest}.}
      \end{cvitems}
    }
%---------------------------------------------------------

\end{cvprojects}